---
title: "esm_244_lab3"
author: "Vienna Saccomanno"
date: "1/24/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(boot)
library(naniar)
library(simputation)
```

##A. Bootstrapping penguin flipper lengths

###1. Get penguin data:

- Data: Penguin sizes collected November 2007, Palmer Station Antarctica LTER). 

- Citation: Gorman K. 2017. Structural size measurements and isotopic signatures of foraging among adult male and female Adélie penguins (Pygoscelis adeliae) nesting along the Palmer Archipelago near Palmer Station, 2007-2009. Environmental Data Initiative. http://dx.doi.org/10.6073/pasta/abc50eed9138b75f54eaada0841b9b86. Dataset accessed 1/29/2018.

```{r}
# Read in data
penguins <- read_csv("penguins.csv")

male_p<-penguins %>% 
  filter(sex=="MALE") #n=27

#Look at distribution - data do not look normally distributed 
ggplot(male_p, aes(x=flipper_length))+
  geom_histogram(bins=10)+
  theme_light()

flippers<- male_p %>% 
  pull(flipper_length)
```

###Creating a function and do bootstrapping
1. must believe that the sample is representitng of the population

```{r}

#selecting mean for bootstrapping with replacement (i.e. if n=27. bootstrap sample = 27 and then calculate the mean)
mean_function<-function(x,i){mean(x[i])} #i = bootstap sample number allowing things to be sequential. x= full sample of 27 penguins

set.seed(10)
boot_10 <- boot(flippers, mean_function, R=10) #will contain bootstrap samples (10)
#original = origiinal mean
#bias = difference in the mean of means
#DIfferent every time, unless you use "set.seed" for one bootstrap
#Use boot_10#t to see all means

boot_100 <- boot(flippers, mean_function, R=100)

#Visualize, need to change vector -> dataframe. Work around is to call ggplot() and keep it empty
ggplot()+
  aes(boot_100$t)+
  geom_histogram()

#New distibution looks a bit more normal
boot_10000 <- boot(flippers, mean_function, R=10000)

ggplot()+
  aes(boot_10000$t)+
  geom_histogram()

#Look for convergence (i.e. does bias and error change as you increase samples?)
  #original      bias    std. error
#t1* 188.1818 -0.01525909    1.351363

boot_100000 <- boot(flippers, mean_function, R=100000)

ggplot()+
  aes(boot_100000$t)+
  geom_histogram()


#    original       bias    std. error
#t1* 188.1818 -0.003828636    1.377794

#Calculate the CI using boot.ci function in the boot package - a common parameter to pull when bootstrapping. 
#Use as a backup to other verifying methods of original sample

boot.ci(boot_10000, conf.=.95)

```

###Missingness with naniar
```{r}

#visualize missingness
vis_miss(airquality)

#visualize by variable - counts of missings
gg_miss_var(airquality, facet = Month)

#Functions to work with GGPlot
#Geom_miss_point()

ggplot(airquality,
       aes(x=Ozone,
           y=Solar.R))+
  geom_miss_point()
#pink y = values where solar radiation was measured but no ozone. Vice versa for pink x

#Facets
ggplot(airquality,
       aes(x=Solar.R,
           y= Temp))+
  geom_miss_point()+
  scale_color_manual(values = c("orange", "purple"))+
  facet_wrap(~Month)
```

